---
title: "Function"
author: "Hannah Hardy"
format: html
editor: visual
---

```{r}
#| include: false

library(tidyverse)
```


# Exercise Functions:

## Question 1

In three or four sentences, explain why constructing a Function. in order to 
execute tasks, is beneficial or advantageous.

*Constructing a function is beneficial because it replaces multiple small tasks
with one complex command to make code look more professional and run efficiently. 
Without functions, code would be lengthy and difficult to interpret for other users.
Functions simplify the code so that a complex task can be done with large numbers 
and/or large amounts of trial runs in a manner that may not be possible to compute by
hand or non-function code.*

## Question 2

Write a function (using r code and structure demonstrated in class) to calculate a z score for a given observed value, a mean, and a standard deviation value. And then use your function to find a z score for the following problem. (Research the internet to find the formula used to calculate a z score)\
Observed value = 25.77, mean = 23.54, standard deviation = 2.442

```{r}
zfunction <- function (obs, mean, sd) {
  z <- (obs - mean) / sd
  
  return(z)
}

zfunction(25.77, 23.54, 2.442)
```


## Question 3

Write a function (using r code and the structure demonstrated in class) to calculate \# the natural log of a number multiplied by the common log of the same number divided by the cube root of a given prime number.\
Use your function to find the answer if the number to be used for both log expressions is 32 and the given prime number is 11.\
Also use R code to round your answer to the nearest tenth

## Question 4

Use and show R coding to calculate the standard deviation for each variable of the data table `mtcars` using the `Special For Loop Method`.
